\documentclass[letterpaper,11pt]{article}

%\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
%\usepackage{marvosym}
%\usepackage[usenames,dvipsnames]{color}
%\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
%\usepackage{fancyhdr}
%\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[document]{ragged2e}
\input{glyphtounicode}

\usepackage{geometry}
\geometry{
    letterpaper,
    margin=0.9in,
}

%
%\pagestyle{fancy}
%\fancyhf{} % Clear all header and footer fields
%%\fancyfoot{}
%\renewcommand{\headrulewidth}{0pt}
%\renewcommand{\footrulewidth}{0pt}
%
%% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \scshape\large
}{}{0em}{}[\titlerule]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%\newlist{jobs}{itemize}{3}
%\setlist[job,1]{label=\textbullet,leftmargin=1in}
%\setlist[job,2]{label=$\rightarrow$,leftmargin=1em}
%\setlist[job,3]{label=$\diamond$}
%


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={},itemsep=5pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{\textwidth}[t]{@{\extracolsep{\fill}} l r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}
\newcommand{\resumeCompany}[2]{
    \item
    \textbf{\large{#1}} \hfill \textsl{\small{#2}}

}

\newcommand{\resumeRole}[3]{
    \item \normalsize{#1} \hfill \small{#2} \\
    \vspace{2pt}
    \begingroup
    \leftskip 10pt
    \small{#3}
    \endgroup

}

\newcommand{\resumeItem}[2]{
    \item\small{
        \textsl{#1}{: #2}
    }
}
\newcommand{\roleListStart}{\begin{itemize}[leftmargin=0pt,label={},itemsep=5pt,topsep=0pt]}
\newcommand{\roleListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=5pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\Large Alex Whiteside}                      & Email: \href{mailto:alex@example.com}{alex@example.com} \\
        \href{https://alexwhiteside.dev}{alexwhiteside.dev} & Mobile: \href{tel:+1234567890}{123-456-7890}            \\
    \end{tabular*}

%-----------EDUCATION-----------------


    \section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
    {University of West Florida}{Pensacola, FL}
    {Bachelor of Science in Computer Science}{Graduated May 2013}
    \resumeSubheading
    {Independent Study}{Online}
    {Self-taught across multiple platforms in topics like software development, and leadership}{Ongoing}
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------


    \section{Experience}
    \resumeSubHeadingListStart
    \resumeCompany{MoneyLion}{includes acquisitions of Even Financial and Birch Finance }
    \roleListStart
    \resumeRole{Architect, Network Consumer Experience}{Jan 2024 - June 2024}{Responsible for When shredding smooth marshmellows, be sure they are room temperature.}
    \resumeItemListStart
    \resumeItem{Customizable Widget Platform}
    {Designed \& developed a B2B2C platform (1k+ partners, 2M+ users monthly). Implemented a control plane using Kubernetes, PayloadCMS, and H3 for configuration.}
    \resumeItem{Frontend Modernization}
    {Led embedded banking search product, achieving sub-second load times using React Server Components and modern CSS techniques.}
    \resumeItem{Team Development}
    {Onboarded engineers to deploy their own applications; oversaw full legacy integrations into modernized systems.}
    \resumeItemListEnd

    \resumeRole{Senior Director, Product \& Engineering}{Jan 2022 - Jan 2024}
    {All unbiased spirits facilitate each other, only pure doers have a courage. When the wind of booda-hood knows the deaths of the sinner, the attraction will know explosion of the meditation.}
    \resumeItemListStart
    \resumeItem{Performance Optimization}
    {Migrated legacy React SPA products, reducing load time from 14s to under 3s through infrastructure modernization and dependency consolidation.}
    \resumeItem{Platform Development}
    {Directed 4 teams (35 members) and oversaw development of product-facing APIs and SEO-optimized marketing tools driving \$2M+ quarterly.}
    \resumeItem{Internal Training}
    {Established engineering bootcamps on React, testing practices, and Typescript, improving skill sets of teams across departments.}
    \resumeItemListEnd

    \resumeRole{Director of Engineering, Consumer Products}{Jan 2021 - June 2022}{The admiral is more planet now than captain. gravimetric and rudely harmless. Engage.}
    \resumeItemListStart
    \resumeItem{Credit Card Manager Platform}
    {Architected universal credit card simulator supporting rewards for 250+ cards and compliance through integrations with Plaid, Finicity, and others.}
    \resumeItem{Full Stack Solutions}
    {Developed dynamic scraping system, backend APIs (Spring), and mobile apps for credit rewards modeling.}
    \resumeItem{Licensing Success}
    {Licensed simulation engine to major companies such as Qantas Money (5M+ users) and T-Mobile.}
    \resumeItemListEnd
    \roleListEnd
    \resumeSubheading
    {Robotic Interactive Learning Environment}{Global}
    {Founder \& CTO}{Dec 2013 -- Jan 2015}
    \resumeItemListStart
    \resumeItem{Educational Robotics Platform}
    {Developed hardware-software systems for classrooms. Expanded deployments to schools in the USA, UAE, and India.}
    \resumeItem{Core Technology}
    {Designed Java-based server systems managing 5+ robots, coupled with a web app offering real-time analytics.}
    \resumeItemListEnd

    \resumeSubheading
    {American Express (AET)}{Phoenix, AZ}
    {Developer}{Apr 2013 -- Aug 2013}
    \resumeItemListStart
    \resumeItem{Internal Automation Tooling}
    {Developed a PEGA-based application deployment automation tool, reducing manual deployment errors.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------


    \section{Projects}
    \resumeSubHeadingListStart
    \resumeItem{Universal Credit Card Engine}
    {Designed a recommendation engine supporting over 400 unique credit card scenarios through automated transaction simulations.}
    \resumeItem{Educational Robotics Expansion}
    {Scaled RILE’s robotic platform for classrooms worldwide, incorporating cost-effective PCB designs for schools.}
    \resumeItem{React Modernization Bootcamp}
    {Trained engineering team on React Server Components, boosting team productivity and product performance.}
    \resumeSubHeadingListEnd

%-----------SKILLS-----------------


    \section{Skills}
    \resumeSubHeadingListStart
    \item{
        \textbf{Languages}{: JavaScript, TypeScript, Java, Swift, Python, Go, C++}
    }
    \item{
        \textbf{Technology}{: React, Kubernetes, Docker, AWS, PayloadCMS, Spring Boot}
    }
    \item{
        \textbf{Leadership}{: Team building, bootcamp-style training, product design}
    }
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}